Automated Topic Naming

### 2011-08-30 ese/ese.tex
updated figures for Weka results and changed wording in paper

% \begin{figure}
%   \centering
%  \includegraphics[width=0.45\textwidth]{figures/unsupervised-bar-f1}
%  \caption{Performance, F1 values (range: 0-1), of unsupervised topic labelling for
%    each NFR and per word-list.}
%   \label{fig:maxdb-unsup-results-f1}
% \end{figure}

@@

\begin{figure}[t]
\centering
% \subfloat[MySQL]{
\includegraphics[width=0.45\textwidth]{figures/both-supervised}
% \label{fig:subfig1}
% }
% \subfloat[MaxDB]{
% \includegraphics[width=0.4\textwidth]{figures/maxdb-supervised}
% \label{fig:subfig2}
% }
\caption[]{ROC value for the best learner per label for MaxDB and MySQL. Values range from $0$--$1$.  Dashed line indicates the performance of a random
classifier.
%\todo[inline]{better discussion}
}
\label{fig:best-learn-per-tag}
\end{figure}

@@

The range of F-measures for MySQL was $0.21$ to $0.77$ with an average
of $0.48$, while MaxDB had a range of $0.17$ to $0.61$ with an average
of $0.39$.

The less-frequently occurring a label, the harder it is to get accurate
results, due to the high noise level. Nevertheless, these results are
better than our previous word-list results of \textsf{exp2} and
\textsf{exp3}, because the ROC values are sufficiently higher in most
cases (other than MaxDB \emph{reliability} and MySQL \emph{efficiency}). The
limitation of the approach we took here is that we assume labels are
independent; however, labels could be correlated with each other. 
The next section (\ref{sec:multilabel})
addresses the issue of a lack of independence and correlation between
labels
using multi-label learners.
%In the next section we will evaluate how well these learners perform
%together.
%\todo[inline]{Comment about correlation, we should link to the Mulan section, perfect segway since Mulan relies on correlation.}

@@

\section{Understanding Software Maintenance Activities} 
\label{sec:analysis}
% \todo[inline]{talk about this topic in one section}
% \todo[inline]{reference project name Nomen more}
%In order to test  our ROC values produced acceptable results, we now turn to
%\emph{applying} those techniques to understand software maintenance
%activities. 
%\todo[inline]{more on intro ... why should the reader care about
 % this. It needs to show how the stuff in the intro (applications) is
 % possible}
%%% XXX NEIL I don't get this.. VVVVV
%\todo[inline]{fix section headings}
As we mentioned in the introduction, a key issue in software maintenance is understanding \emph{why} a system has evolved the way it has~\cite{aranda09icse}. 
In this section we demonstrate the value of labelled topic extraction
in addressing this issue. 
% more why
Labelled topics address \emph{why}  because they show reasons why changes
occurred rather than \emph{how}. 
The \emph{how} of a change is the change itself, the purpose or
\emph{why} is what we are after.
We investigate the history of the two large-scale database systems that we studied. 
We use our technique to show the topic of development efforts over time in each project.
%We evaluated two research questions using the ground truth data that we annotated by hand:
We motivated our investigation with three research questions:
\begin{enumerate}
\item \emph{Do NFR frequencies change over time?} If a particular NFR
  was of more interest at one point in the life-cycle than another,
  this suggests that development activity shifted focus. For example,
  if a developer expected to see a recent focus on \emph{reliability},
  but instead \emph{usability} dominated, they might re-prioritize
  upcoming work items.

@@

We now address our research questions:

>>>>

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.45\textwidth]{figures/both-supervised}
\caption[]{ROC value for the best learner per label for MaxDB, MySQL and PgSQL. Values range from $0$--$1$.  Dashed line indicates the performance of a random
classifier.
}
\label{fig:best-learn-per-tag}
\end{figure}

@@

The range of F-measures for MySQL was $0.21$ to $0.77$ with an average
of $0.48$. MaxDB had a range of $0.17$ to $0.61$ with an average
of $0.39$. Finally, PostgreSQL had a range of $0.04$ to $0.9$ and an average of $0.43$.

The less-frequently occurring a label, the harder it is to get accurate
results, due to the high noise level. Nevertheless, these results are
better than our previous word-list results of \textsf{exp2} and
\textsf{exp3}, because the ROC values are sufficiently higher in most
cases (other than MaxDB \emph{reliability}, MySQL \emph{efficiency}, and PgSQL \emph{usability}). The
limitation of the approach we took here is that we assume labels are
independent; however, labels could be correlated with each other. 
The next section (\ref{sec:multilabel})
addresses the issue of a lack of independence and correlation between
labels
using multi-label learners.
%In the next section we will evaluate how well these learners perform
%together.
%\todo[inline]{Comment about correlation, we should link to the Mulan section, perfect segway since Mulan relies on correlation.}

@@

\section{Understanding Software Maintenance Activities} 
\label{sec:analysis}
As we mentioned in the introduction, a key issue in software maintenance is understanding \emph{why} a system has evolved the way it has~\cite{aranda09icse}. 
In this section we demonstrate the value of labelled topic extraction
in addressing this issue. 
% more why
Labelled topics address \emph{why}  because they show reasons why changes
occurred rather than \emph{how}. 
The \emph{how} of a change is the change itself, the purpose or
\emph{why} is what we are after.
We investigate the history of the two large-scale database systems that we studied. 
We use our technique to show the topic of development efforts over time in each project.
%We evaluated two research questions using the ground truth data that we annotated by hand:
We motivated our investigation with three research questions:
\begin{enumerate}
\item \emph{Do NFR frequencies change over time?} If a particular NFR
  was of more interest at one point in the life-cycle than another,
  this suggests that development activity shifted focus. For example,
  if a developer expected to see a recent focus on \emph{reliability},
  but instead \emph{usability} dominated, they might re-prioritize
  upcoming work items.

@@

In the following sections we turn to our research questions:
